Checkpoint 4

### 2020-04-29 Checkpoint 4.Rmd
4 models

```{r}
Finaldata<-read.csv("time_series_final_Data.csv")
```

@@

>>>>

```{r}
Finaldata<-read_csv("time_series_final_Data.csv")
```

@@

#Fed's visualizations:
```{r}
#for visuals
install.packages("ggforce")
library(ggforce)
ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 1) + 
    theme(legend.position = "none")
```

```{r}
ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 2) + 
    theme(legend.position = "none")
```

```{r}
ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 3) + 
    theme(legend.position = "none")
```

```{r}
ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 4) + 
    theme(legend.position = "none")
```

```{r}
ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 5) + 
    theme(legend.position = "none")
```

```{r}
ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 6) + 
    theme(legend.position = "none")
```

#Fed's Models:

Variables of interest:
- % white
- postive rate (out of the tested)

```{r}
set.seed(454)
glimpse(Finaldata)
model_data<-Finaldata%>%
  mutate(Date = as.numeric(Day))%>%
  mutate(positive_rate = positive/ totalTestResults)%>%
  select(State, ChinaVirusInterest, Day, percent_white,positive_rate)
model_data<- na.omit(model_data)

colSums(is.na(model_data))

model_10 <- stan_glmer(
  ChinaVirusInterest ~ Day + (1 | State) + percent_white,
  data = model_data, family = gaussian, chains = 4, iter = 1000
)
```
```{r}
head(data.frame(summary(model_10)),-2)
```

```{r}
# Store the chains
model_10_df <- as.array(model_10) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_10_df <- model_10_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_10_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```
```{r}
set.seed(454)
#random intercept and random slope, percent white
model_11 <- stan_glmer(
  ChinaVirusInterest ~ (Day | State) + percent_white,
  data = model_data, family = gaussian, chains = 4, iter = 3000
)
```
```{r}
head(data.frame(summary(model_11)),-2)
```

```{r}
# Store the chains
model_11_df <- as.array(model_11) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_11_df <- model_11_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_10_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

```{r}
set.seed(454)

model_12<- stan_glmer(
  ChinaVirusInterest ~ Day + (1 | State) + percent_white +positive_rate,
  data = model_data, family = gaussian, chains = 4, iter = 3000
)
```
```{r}
head(data.frame(summary(model_12)),-2)
```

```{r}
# Store the chains
model_12_df <- as.array(model_12) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_12_df <- model_12_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_12_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

```{r}
set.seed(454)
#random intercept and random slope, percent white and positive rate = positive/ total tests
#iterations might be low need to sample up if we want to make the models better
model_13 <- stan_glmer(
  ChinaVirusInterest ~ (Day | State) + percent_white +positive_rate,
  data = model_data, family = gaussian, chains = 4, iter = 3000
)
```
```{r}
head(data.frame(summary(model_13)),-2)
```

```{r}
# Store the chains
model_13_df <- as.array(model_13) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_13_df <- model_13_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_13_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```
